Modeling the impacts of replacing car trips with combined public transport and cycling: \ Reproducible methods, results and actionable evidence from the XXX project

### 2023-11-28 paper/PaperCEUS/PaperCEUS.Rmd
Modeling 1L

---
title: "Modelling the impacts of replacing car trips with combined public transport and cycling: \ Reproducible methods, results and actionable evidence from the XXX project"
# subtitle: "Reproducible methods, results and actionable evidence from the XXX project"
author:
  - name: Rosa Félix\corref{cor1}
    affiliation: CERIS
    correspondingauthor: true
    # footnote: 1
    email: rosamfelix@tecnico.ulisboa.pt
  - name: Filipe Moura
    affiliation: CERIS
    email: fmoura@tecnico.ulisboa.pt
  - name: Robin Lovelace
    affiliation: ITS
    email: r.lovelace@uleeds.uk
address:
  - code: CERIS
    address: "CERIS, Instituto Superior Técnico - Universidade de Lisboa, Av Rovisco Pais 1, 1049-001 Lisboa, Portugal"
  - code: ITS
    address: "Institute for Transport Studies, University of Leeds. 34-40 University Rd, Leeds LS2 9JT, UK"
abstract: |
  A high proportion of car trips can be replaced by a combination of public transit and cycling for the first-and-last mile. This paper estimates the potential for cycling combined with public transit (PT) as a substitute for car trips in the Lisbon metropolitan area and assesses its socio-environmental impacts using open data and open source tools.
  A decision support tool that facilitates the design and development of a metropolitan cycling network was developed (_XXX_). The social and environmental impacts were assessed using the _HEAT for Cycling_ and the _HEAT as a Service_ tools. The impacts of shifting car trips to PT were also estimated and monetized.
  The results indicate that 10% of trips could be made by bicycle + PT combination. Shifting to cycling for the first-and-last mile stages can reduce annual CO~2~eq emissions from 3,000 to 7,500 tons/day, while for the PT leg, the transfer from car avoids of up to 20,500 tons of CO~2~eq emissions per year. The estimated socio-environmental benefits are of €125 million to €325 million over 10 years.
  This evidence can support policymakers to prioritize interventions that reduce the reliance on private motor vehicles.
  \
keywords: 
  - Active transport
  - Intermodality
  - First and last mile
  - Health economic assessment
  - Environmental impacts
  - Open data and methods
journal: "Computers, Environment and Urban Studies"
date: "`r Sys.Date()`"
classoption: review, doubleblind, 3p, authoryear #change later to preprint instead of review
bibliography: bibliography.bib
biblio-style: elsarticle-harv
linenumbers: true
numbersections: true
# Use a CSL with `citation_package = "default"`
csl: https://www.zotero.org/styles/computers-environment-and-urban-systems
# csl: computers-environment-and-urban-systems.csl
# csl: trd_test.csl
preamble: |
  \biboptions{authoryear}
  \usepackage{url}
  \usepackage{float}
  \usepackage{booktabs}
  \usepackage{longtable}
  \usepackage{makecell}
  \usepackage{multirow}
output: 
  rticles::elsevier_article:
    keep_tex: yes
    citation_package: "default" #ou nenhum
    latex_engine: xelatex
    extra_dependencies: "subfig"
#   bookdown::word_document2:
#     fig_caption: true
# always_allow_html: true
urlcolor: blue
citecolor: blue
linkcolor: blue
# natbiboptions: longnamesfirst,angle,semicolon
---

@@

[^1]: See https://xxx.xxx. *For double blind peer-review process, the authors decided to truncate the name and references to this tool*.
<!-- [^1]: See [biclar.tmlmobilidade.pt](https://biclar.tmlmobilidade.pt/). -->

@@

## Modelling Origin-Destination trips

@@

## Modelling routes

The mobility survey collects the origin and destination of trips but does not include the respective routes.
Modelling the realistic cycling + PT routes between OD pairs depends on assumptions regarding the characteristics of the cycling and road networks and the location of public transport interfaces.
Other constraints regarding the behavior of potential cyclists determine the routing results.
For example, such restrictions can favor low speed, low traffic streets, more direct routes, and less steep paths, among others, which are suitable for cycling.

@@

## Modelling intermodality

>>>>

---
title: "Modeling the impacts of replacing car trips with combined public transport and cycling: \ Reproducible methods, results and actionable evidence from the XXX project"
# subtitle: "Reproducible methods, results and actionable evidence from the XXX project"
author:
  - name: Rosa Félix\corref{cor1}
    affiliation: CERIS
    correspondingauthor: true
    # footnote: 1
    email: rosamfelix@tecnico.ulisboa.pt
  - name: Filipe Moura
    affiliation: CERIS
    email: fmoura@tecnico.ulisboa.pt
  - name: Robin Lovelace
    affiliation: ITS
    email: r.lovelace@uleeds.uk
address:
  - code: CERIS
    address: "CERIS, Instituto Superior Técnico - Universidade de Lisboa, Av Rovisco Pais 1, 1049-001 Lisboa, Portugal"
  - code: ITS
    address: "Institute for Transport Studies, University of Leeds. 34-40 University Rd, Leeds LS2 9JT, UK"
abstract: |
  A high proportion of car trips can be replaced by a combination of public transit and cycling for the first-and-last mile. This paper estimates the potential for cycling combined with public transit (PT) as a substitute for car trips in the Lisbon metropolitan area and assesses its socio-environmental impacts using open data and open source tools.
  A decision support tool that facilitates the design and development of a metropolitan cycling network was developed (_XXX_). The social and environmental impacts were assessed using the _HEAT for Cycling_ and the _HEAT as a Service_ tools. The impacts of shifting car trips to PT were also estimated and monetized.
  The results indicate that 10% of trips could be made by bicycle + PT combination. Shifting to cycling for the first-and-last mile stages can reduce annual CO~2~eq emissions from 3,000 to 7,500 tons/day, while for the PT leg, the transfer from car avoids of up to 20,500 tons of CO~2~eq emissions per year. The estimated socio-environmental benefits are of €125 million to €325 million over 10 years.
  This evidence can support policymakers to prioritize interventions that reduce the reliance on private motor vehicles.
  \
keywords: 
  - Active transport
  - Intermodality
  - First and last mile
  - Health economic assessment
  - Environmental impacts
  - Open data and methods
journal: "Computers, Environment and Urban Studies"
date: "`r Sys.Date()`"
classoption: review, doubleblind, 3p, authoryear #change later to preprint instead of review
bibliography: bibliography.bib
biblio-style: elsarticle-harv
linenumbers: true
numbersections: true
# Use a CSL with `citation_package = "default"`
csl: https://www.zotero.org/styles/computers-environment-and-urban-systems
# csl: computers-environment-and-urban-systems.csl
# csl: trd_test.csl
preamble: |
  \biboptions{authoryear}
  \usepackage{url}
  \usepackage{float}
  \usepackage{booktabs}
  \usepackage{longtable}
  \usepackage{makecell}
  \usepackage{multirow}
output: 
  rticles::elsevier_article:
    keep_tex: yes
    citation_package: "default" #ou nenhum
    latex_engine: xelatex
    extra_dependencies: "subfig"
#   bookdown::word_document2:
#     fig_caption: true
# always_allow_html: true
urlcolor: blue
citecolor: blue
linkcolor: blue
# natbiboptions: longnamesfirst,angle,semicolon
---

@@

[^1]: See xxx.xxx. *For double blind peer-review process, the authors decided to truncate the name and references to this tool*.
<!-- [^1]: See [biclar.tmlmobilidade.pt](https://biclar.tmlmobilidade.pt/). -->

@@

## Modeling Origin-Destination trips

@@

## Modeling routes

The mobility survey collects the origin and destination of trips but does not include the respective routes.
Modeling the realistic cycling + PT routes between OD pairs depends on assumptions regarding the characteristics of the cycling and road networks and the location of public transport interfaces.
Other constraints regarding the behavior of potential cyclists determine the routing results.
For example, such restrictions can favor low speed, low traffic streets, more direct routes, and less steep paths, among others, which are suitable for cycling.

@@

## Modeling intermodality
